Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-29 writeup/gz_hubble_data.tex

In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions. The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 5~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift. This requirement placed on both images is not met by a significant number of galaxies for questions beyond Task~01. The FERENGI images classified do not have sufficient numbers of objects in the surface brightness/redshift bins to accurately measure if the relation between vote fractions and redshift is single-valued.

for this reason we only offer debiased vote fractions for Task~01 (smooth/features/artifact).

{\note Perhaps compute number of galaxies that can be fit to zeta for each question, show a table? overkill?}

In Section \ref{sec:ferengi_bar} we show results of an attempt to measure $\zeta$ for $\rm p_{bar}$.

>>>>

In the FERENGI data, these numbers severely limit the amount of information we can extract for the higher-tier questions. The debiasing technique used (Section~\ref{ssec:zeta}) require that at least 10~users answer each question for a galaxy image at $z=0.3$ \emph{and} its image at higher redshift. This requirement is by default met by all galaxies when analyzing the first question, since it is asked of all users. This requirement is often \emph{not} met for questions beyond Task~01; on average 59\% of the galaxies do not have sufficient data to measure a correction, as compared to 2\% acheived for Task~01 (see Table~\ref{tbl:ferengi_corrections}). Of the remaining FERENGI galaxies which did meet this requirement, the data available in each redshift-surface brightness bin were not tightly correlated between $p_{task,z=0.3}$ and $p_{task,z}$, and relationships between the two could not be fit with high confidence. We use these galaxies to compute $\zeta$ for each Task, and find the p-values for the resulting functions between $placeholder < p < placeholder$, which we consider insufficient for deriving a correction. We show an example of this in Section \ref{sec:ferengi_bar}, where we show results of measuring $\zeta$ for $p_{\rm bar}$ in Task~03. For this reason we only offer debiased vote fractions for Task~01 (smooth/features/artifact).
